Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-17 paper/paper.tex
preliminaries (1)

The online \emph{Balanced Re-Partitioning} problem (\OBRP{}) is defined as
follows. We are given a set of $n$ nodes,
initially arbitrarily partitioned into $\ell$~clusters,
each of size~$k$.
The input consists of a sequence of pairwise communication requests
$\sigma = (u_1,v_1),$ $(u_2,v_2),$ $(u_3,v_3), \ldots$,
where a pair $(u_t,v_t)$ indicates that nodes $u_t$ and $v_t$ exchange a fixed amount of data.
Nodes in $C \subset V$ are \emph{collocated}
if they reside in the same cluster.
An algorithm serves a communication request between two nodes
either \emph{locally} at cost~0
if they are collocated,
 or \emph{remotely} at cost~1
 if they are located in different clusters.
 We refer to the two types of requests as \emph{internal}
 and \emph{external} requests, respectively.
Before serving a request,
an online algorithm can \emph{re-partition},
i.e.,
it may (optionally) move some nodes into clusters different than their current assigneclusters while respecting the capacity of every cluster. he re-partition is executed,
the algorithm serves the  request
the communication request between two  nodes at cost~0 if they are collocated,
or at cost~1 if they are located in different clusters.
The cost of migrating a node from one cluster to another
is~$\alpha \in \mathbb{Z}^+$.
For any algorithm $ALG$,
its cost,
denoted by $ALG(\sigma)$,
is the total cost of communications and
the cost of migrations performed by $ALG$ while serving the sequence $\sigma$.

An algorithm that  keeps all components collocated is \emph{component-respecting}.
%
A \emph{component} is a subset of frequently communicating nodes.   ly,                                                   ,every node is trivially a \emph{singleton} component.
We grow components similar fashion to previous approaches~\cite{repartition-disc}.
which proved to be an effective techique for mimi                                                                it always keep.
That is,
if the algorithm needs to move a node,
it moves the whole component containing the node to the sameemph{component -respecting}, i.e., it maintains the invariant that nodes of each component are collocated in the same cluster.
%We say that the request $(u,v)$ is \emph{external}, if the algorithm is in the configuration, where $u$ and $v$ are located at different clusters.
%
This is achieved by opting a sequence of  partitions (a.k.a.~configurations)
such that frequently communicating nodes (from different clusters)
are relocated to the same cluster before they inflict too much communication cost.
A \emph{reconfiguration} (i.e., re-partitioning) is performed by
 migrating) nodes betwen clusters at a cost.   ,s to jointly minimize communication and migration costs while serving the sequence.

>>>>

The online \emph{Balanced RePartitioning} problem (\OBRP{}) is defined as
follows. We are given a set of $n$ nodes,
initially arbitrarily partitioned into $\ell$~clusters,
each of size~$k$.
The input consists of a sequence of pairwise communication requests
$\sigma = (u_1,v_1),$ $(u_2,v_2),$ $(u_3,v_3), \ldots$,
where a pair $(u_t,v_t)$ indicates that nodes $u_t$ and $v_t$ exchange a fixed amount of data.
Nodes in $C \subset V$ are \emph{collocated}
if they reside in the same cluster.
An algorithm serves a communication request between two nodes
either \emph{locally} at cost~0
if they are collocated,
or \emph{remotely} at cost~1
if they are located in different clusters.
We refer to the two types of requests as \emph{internal}
and \emph{external} requests, respectively.
Before serving a request,
an online algorithm may \emph{re-partition},
%(i.e., \emph{reconfigure}).
i.e.,
it may (optionally) move some nodes into clusters different than their current clusters while respecting the capacity of every cluster. 
Only after a re-partition is completed,
the algorithm serves the  request.
The cost of migrating a node from one cluster to another
is~$\alpha \in \mathbb{Z}^+$.
For any algorithm $ALG$,
its cost,
denoted by $ALG(\sigma)$,
is the total cost of communications and
the cost of migrations performed by $ALG$ while serving the sequence $\sigma$.

%\maciek{I just copied useful sentences. This section is TODO}
%An algorithm that  keeps all components collocated is \emph{component-respecting}.
%
A \emph{component} is a subset of frequently communicating nodes.
Initially,
every node is trivially a \emph{singleton} component.
We grow components similar to previous approaches~\cite{repartition-disc},
which proved to be an effective technique for mimicking an optimal offline algorithm.
An algorithm is \emph{component-respecting}
if it always keeps nodes that  belong to the same component collocated.
That is,
if the algorithm needs to move a node,
it moves the whole component containing the node.
%We say that the request $(u,v)$ is \emph{external}, if the algorithm is in the configuration, where $u$ and $v$ are located at different clusters.
%This is achieved by opting a sequence of  partitions (a.k.a.~configurations)
%such that frequently communicating nodes (from different clusters)
%are relocated to the same cluster before they inflict too much communication cost.
%A \emph{reconfiguration} (i.e.,\emph{ re-partitioning})
%is performed by migrating nodes between clusters,
%at the total cost of individual node migrations.
The objective is to jointly minimize communication and migration costs while serving the sequence.
